---
title: "Experimental plan"
author: "Rachael Remmington"
---

Now that you have been developing a research question over the last few months, the next step is to design a set of experiments that will specifically test your research aims.

We are often focused on the “cookbook” aspect of experiments – the protocols and steps required to conduct each experiment. However, it’s critical to spend time designing your overall experimental approach and the finer details to ensure that your research will produce robust data that can be clearly analysed without bias. When we test specific questions, we want to avoid statistical issues such as “noise” and "confounding" factors.

Terry Neeman will be delivering a workshop to help you strengthen your experimental plan – both in terms of your proposed design, and to help you more clearly and accurately explain the rationale and set-up of your experiments. This workshop will help you apply the principles taught in BIOL8291 to your own experiment. To prepare, you will create an outline of your experimental plan, focusing on the statistical framework of your design.

Below is an outline of questions for you to answer/justify for each part of your experimental plan. You will also need to draw two figures (digital drawings preferred) for each aim that show:

1) a simple overview of the experimental plan related to the research aim,
2) a detailed “snap-shot” of the experimental set up (i.e., how will the plates, plants, etc. be arranged? Will there be a row-column design? Blocking? Randomization? What treatments will be applied and how many replicates will be tested?)

You can access the template for the experimental plan on Wattle or a copy can be found within this repository. [DOWNLOAD NOW]("3. Statistical Methods in Biology - Chapter 3.pdf"). The template is laid out below as follows:

## Research Question(s)?

```{r}
#input question here
```

## Experimental Aims?

For each experiment explain the overall experimental approach (1-3 sentences + overview diagram) list:

1) the response variables/outcome measure(s) for the experiment
2) the experimental factor(s) of interest
3) the experimental conditions (groups for comparisons), and the number of replicates/sample size for each condition
4) the experimental control(s)
5) are their any potentially confounding factors (“nuisance factors”)? Briefly explain how they will be tracked/or mitigated

Briefly explain the design of the experiment and provide a diagram that shows a “snap shot” of the experimental set-up (e.g., how all the plants under different experimental conditions will be arranged, all the plates in the lab, a flow chart of computational steps, etc.). Make sure to consider and include relevant design aspects like blocking, randomisation, as well as to clearly indicate treatments, replicate numbers, and controls.

> TIP: Start thinking about how you will analyse your data:  
                "what statistical tests would you use?"
                
                
## Importing data


```{r}



```



## Visualising data

```{r}

```



## Reporting

```{r}

```

