---
title: "RMarkdown tips and tricks"
---

<!-- # ```{r child = "README/README.Rmd"} -->
<!-- # #list.files() -->
<!-- # ``` -->

Last week we began to set up our projects using RMarkdown and R code so that we are ready for Terry Newmans sample/survey design session. 

Now this is postponed till next week we can finish this off. 

# RStudio project file

- https://r4ds.had.co.nz/workflow-projects.html

```{r include=FALSE}
# automatically create a bib database for R packages
knitr::write_bib(c(
  .packages(), 'bookdown', 'knitr', 'rmarkdown'
), 'packages.bib')
```

## git ignore file

```
# History files
.Rhistory
.Rapp.history

# Session Data files
.RData

# User-specific files
.Ruserdata

# Example code in package build process
*-Ex.R

# Output files from R CMD build
/*.tar.gz

# Output files from R CMD check
/*.Rcheck/

# RStudio files
.Rproj.user/

# produced vignettes
vignettes/*.html
vignettes/*.pdf

# OAuth2 token, see https://github.com/hadley/httr/releases/tag/v0.3
.httr-oauth

# knitr and R markdown default cache directories
*_cache/
/cache/

# Temporary files created by R markdown
*.utf8.md
*.knit.md

# R Environment Variables
.Renviron

#notes
/notes2022/
/_main/
/libs/
/experimental_plan/
/Presentation/
/data/
```

```{r child = "README/README.Rmd"}
#list.files()
```

### Quick overview of last week

1. Run the R chunk below and check that you have all the packages running from last week.

```{r}
library(rmarkdown)
library(rticles)
library(bookdown)
library(bookdownplus)
library(tidyverse)
library(readxl)
```

2. Can you import the data set you found last week in class?

```{r}
#read.csv
#read.xl
#example from 
```

- What options did we have?
- Here I will take the following dataset and extend this to include some code and plots for the data

3. Follow along with the next chapter....



4.




