---
title: "Data reporting in RMarkdown."
subtitle: " A quick demo"
output: html_notebook
---

# RMarkdown reports

We should all know what these are and how to render a report in RMarkdown. Next we will produce a RMarkdown document for the question we have been working on ready to add data and other sampling design information.

```{r}
#general packages used
library(tidyverse)
```

What does this tell us about how RProjects and other funky things work?

3. Data import

```{r}
dat <- read.csv("data/Analysis_ardMods.csv")
glimpse(dat)
```


4. Data visualisation

```{r}
# table(dat$Well.Position)
mean(dat$Delta.Ct.Mean, na.rm = TRUE)
sd(dat$Delta.Ct.Mean, na.rm = TRUE)

hist(dat$Delta.Ct.Mean)
```


5. Tidyverse approach



6.    ggplot

Tasks ready for next week:

1. Outcome and predictor variables



3. Other studies with same sampling design

5. Other reference material.

7. Read a cool sampling design/issue paper

Watch this short (ish video) as a summary of what you should understand so far.