<!-- # --- -->
<!-- # title: "Study/sampling design lecture information" -->
<!-- # subtitle: "Recreated in RMarkdown by Anthony Davidson" -->
<!-- # author: Terri Newman -->
<!-- # --- -->

# Sampling design

Outcome vs experimental factors matter. How we construct models is directly related to the underlying structure of the data we have collected.

```{r message = FALSE, warning=FALSE}
#general packages used
library(tidyverse)
library(knitr)
library(gridExtra)
library(here)
```

## Terry's lecture in RMarkdown

Understanding variance is very important for building statistical models. But what it is really about is structuring and generating reproducible experiments.

```{r fig.align='center'}
knitr::include_graphics("study_experiment_design/Experimental-plan-workshop Terry Neeman 17 May 2002.pdf")
```

We should all know what these are and how to render a report in RMarkdown. Next we will produce a RMarkdown document for the question we have been working on ready to add data and other sampling design information. 

1. Outcome and predictor variables
2. Statistical model fitting
3. Visual results

<!-- Two colomns with images from talk on right side? -->

### How would you design your experiment?

What will the actual design look like? How are the treatments and samples laid out within the experimental layout.

### Model selection

Defining models and the notation associated with the aims and hypotheses of the research project is an important part of communicating reproducing results.

#### Model construction

Went we are testing hypothesis we can only disprove the null hypothesis. To do this we can fit a series of linear models increasing in complexity as we ask our research questions.

##### Null model

In statistical tests the null model can be defined as almost anything however most commonly this is the simplist model that assumes no relationship between the outcome and the treatments.

$$ null model: lm(predictor = 0) $$
##### Different mean



##### Interaction

More complex model.


$$ model_1 = lm(activity \equiv GBP8 + (1|litter) + (1|mouseID)) $$