---
title: "Data reporting in RMarkdown."
subtitle: " A quick demo"
output: html_notebook
---

# RMarkdown reports

We should all know what these are and how to render/generate a  report or document in RMarkdown. 

The next we will produce a RMarkdown document for the question we have been working on ready to add data and other sampling design information.

```{r}
#general packages used
library(tidyverse)
```

What does this tell us about how RProjects and other funky things work?

3. Data import

```{r}
dat <- read.csv("data/Analysis_ardMods.csv")
glimpse(dat)
variable.names(dat)

length(unique(dat$Well.Position))

# outcome <- dat$

table(dat$Omit)

removedData <- dat %>%
  filter(Omit != "false")

head(removedData)
```


4. Data visualisation

```{r}
# table(dat$Well.Position)
mean(dat$Delta.Ct.Mean, na.rm = TRUE)
sd(dat$Delta.Ct.Mean, na.rm = TRUE)

hist(dat$Delta.Ct.Mean)
```

3. Data import

```{r}
dat <- read.csv("data/Analysis_ardMods.csv")
```


4. Data visualisation

```{r}
# table(dat$Well.Position)
mean(dat$Delta.Ct.Mean, na.rm = TRUE)
sd(dat$Delta.Ct.Mean, na.rm = TRUE)

hist(dat$Delta.Ct.Mean)
```


5. Tidyverse approach

```{r}
variable.names(dat)

#sample name
# table(dat$Sample.Name)
table(dat$Target.Name)
mean(as.numeric(dat$CT), na.rm = TRUE)

##sumarise over Target Name and find n, mean, mode, median, sd, etc for each of the target names?

```

6. Nicer plots using `ggplot`

5. Tidyverse approach

```{r}
#tidy data
#tibble

```


6.    ggplot

Much easier to work this this and tidyverse


7. Read a cool sampling design/issue paper
