
```{r}
#general packages used
library(tidyverse)
```

We should all know what these are and how to render a report in RMarkdown. Next we will produce a RMarkdown document for the question we have been working on ready to add data and other sampling design information. 

1. Outcome and predictor variables
2. Other study examples and code
3. Other studies with same sampling design
4. Other reference material.
5. Read a cool sampling design/issue paper

# Power analysis

Watch this short (ish video) as a summary of what you should understand so far.
What does this tell us about how RProjects and other funky things work?


```{r}
library(stats)
power.anova.test(groups = 4, n = 5, between.var = 1, within.var = 3)
# Power = 0.3535594

power.anova.test(groups = 4, between.var = 1, within.var = 3,
                 power = .80)
# n = 11.92613

## Assume we have prior knowledge of the group means:
groupmeans <- c(120, 130, 140, 150)
power.anova.test(groups = length(groupmeans),
                 between.var = var(groupmeans),
                 within.var = 500, power = .90) # n = 15.18834
```


<!-- Watch this short (ish video) as a summary of what you should understand so far. -->

I can not find the additional code from last year but this is a slight variation on the project.

```{r}
knitr::include_app("https://mathiasharrer.shinyapps.io/power_calculator_meta_analysis/", height = "1500px") 
```

## Meta-analysis power test

```{r}
# The included numbers will per calculate power for a meta-analysis to detect a summary effect size of 0.2, with an average sample size per group of = 50, a total of 15 effect sizes, and moderate heterogeneity.

es <- 0.2 # Enter your summary effect size
as <- 50  # Average per number per group
mk <- 15  # Number of effect sizes
hg <- 1   # Heterogeniety (".33" for small, "1" for moderate, & "3" for large)

eq1 <- ((as+as)/((as)*(as))) + ((es^2)/(2*(as+as)))
eq2 <- hg*(eq1)
eq3 <- eq2+eq1
eq4 <- eq3/mk
eq5 <- (es/sqrt(eq4))
Power <- (1-pnorm(1.96-eq5)) # Two-tailed
Power
```

#### Next steps

Collect some sample data and application.

z