---
output: github_document
keep_md: true
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

# BIOL8700_setup_2022

<!-- badges: start -->
<!-- badges: end -->

The goal of BIOL8700_setup_2022 is to setup and generate documents using RStudio, RMarkdown and github

## Tools

This is a _sample_ book written in **Markdown** and includes embedded R code. This combination of programming languages is included in the RMarkdown package. We use this and a variation of other RMarkdown packages to make the most of reproducible reporting in R.

## Data importing

There are scripts and code included within this repository to import data from csv and excel files from local and online locations.

## Results

You can also embed plots, code and data in an RMarkdown document. The core results of this repository are as follows:

```{r}

```

In that case, don't forget to commit and push the resulting figure files, so they display on GitHub.
